Exploring Uncharted Territories - Predicting Activty Cliffs in Structure-Activity Landscapes

### 2012-07-25 rebuttal.tex

The manuscript has been thoroughly proof read and references included where appropriate

\textbf{(3) The derivation of RF models is essentially not described (except of making reference to
  default parameters settings in R). It remains largely unclear how these models were developed. }

The text has been updated to be more specific on the development of the random forest model.

\textbf{(4) The selection of training and test sets should be clearly specified in the Methods section. For
example, how were the RF models trained and evaluated for which predictions of pair-wise SALI values
are reported in Figure 2? It is hoped that the reported SALI values were not predicted for the
training data.}

XXX

\textbf{(5) No support is provided for the assumption that the RF models “are relatively robust even for
datasets of small size”. In fact, the author later on states several times that limited model
quality might be due to the use of small compound sets. Appropriate validation will be essential
here.
}

XXX

### 2012-07-25 paper.tex
Added in tset/pset split results and updated figures for Cavalli dataset

\documentclass[letterpaper, 12pt]{article}
%%\documentclass[letterpaper, 11pt, twocolumn]{article}
\usepackage{url}
\usepackage{ctable}
\usepackage{overcite}
\usepackage{amsmath,amssymb}      % for \AA etc
\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{fullpage, times}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{longtable}

@@

\ctable[cap={}, caption={Performance metrics for the random forest
  models built for the datasets used in this study. RMSE and $R^2$ are
based on out-of-bag data\cite{Breiman:1984aa}},
label={tab:rfmodel-results}]
{lrcrr}
{}
{\FL
Dataset & Y-range & Aggregation Function & RMSE & $R^2$ 
\ML
Cavalli & 7.21 & $f_{\textrm{diff}}$ & 1.11& 0.57\NN
        & & $f_{\textrm{mean}}$ & 0.98& 0.67\NN
        & & $f_{\textrm{geom}}$ & 1.01& 0.65\NN \NN
Costanzo & 288.03& $f_{\textrm{diff}}$ & 12.88& 0.24\NN
       & & $f_{\textrm{mean}}$ & 13.56& 0.17\NN \NN
Kalla & 88.25 & $f_{\textrm{diff}}$ & 7.51& 0.62\NN
      &  & $f_{\textrm{mean}}$ & 8.26& 0.53\NN \NN
Dai & 32.71 & $f_{\textrm{diff}}$ & 2.60& 0.44\NN
     &   & $f_{\textrm{mean}}$ & 2.67& 0.41
\LL
}

>>>>

\documentclass[letterpaper, 12pt]{article}
%%\documentclass[letterpaper, 11pt, twocolumn]{article}
\usepackage{url}
\usepackage{ctable}
\usepackage{overcite}
\usepackage{amsmath,amssymb}      % for \AA etc
\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{fullpage, times}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{longtable}
%%\usepackage{booktabs}

@@

\ctable[cap={}, caption={Performance metrics for the random forest
  models built for the datasets used in this study. Training RMSE and $R^2$ are
based on out-of-bag data\cite{Breiman:1984aa} and test metrics are based on a separate
hold out set. },
label={tab:rfmodel-results}]
{lrcrrrr}
{
\tnote{Y-range is calculated using the entire dataset for each study.}
}
{\FL
        &         &                      & \multicolumn{2}{c}{Training} & \multicolumn{2}{c}{Test}
\NN
\cmidrule{4-5}  \cmidrule{6-7}
Dataset & Y-range\tmark & Aggregation Function & RMSE & $R^2$ & RMSE & $R^2$   
\ML
Cavalli & 7.21 & $f_{\textrm{diff}}$ & 1.16& 0.54 & 1.07& 0.56\NN
        & & $f_{\textrm{mean}}$      & 1.03& 0.64 & 1.01& 0.58\NN
        & & $f_{\textrm{geom}}$      & 1.07& 0.61 & 1.01& 0.59\NN \NN
Costanzo & 288.03& $f_{\textrm{diff}}$ & 12.88& 0.24 & & \NN
       & & $f_{\textrm{mean}}$ & 13.56& 0.17 & & \NN \NN
Kalla & 88.25 & $f_{\textrm{diff}}$ & 7.51& 0.62 & & \NN
      &  & $f_{\textrm{mean}}$ & 8.26& 0.53  & & \NN \NN
Dai & 32.71 & $f_{\textrm{diff}}$ & 2.60& 0.44 & & \NN
     &   & $f_{\textrm{mean}}$ & 2.67& 0.41  & & 
\LL
}
